Learning action models with minimal observability

### 2018-08-05 doc/aij18/motivation.tex
corregido #domains y minor comment

On the other hand, a striking figure of Table \ref{table:models_comparison2} that emphasizes a relevant feature of \FAMA is the small size of the training dataset it requires in comparison to other approaches. Unlike extensive-data ML approaches, our work explores an alternative research direction to learn sound models from small amounts of plan traces. This is an important advantage, particularly in domains in which it is costly or impossible to obtain a significant number of training samples. Unlike \CAMA, our approach does not require human intervention to label samples as it is able to learn from very small datasets.

Finally, as it will be shown in section \ref{sec:experiments}, \FAMA is exhaustively evaluated, syntactically and semantically, over a wide range of domains (13 domains compared to the scarce number of tested domains of the rest of the approaches in Table \ref{table:models_comparison2}) and uses exclusively an \emph{off-the shelf} classical planner so it can benefit straightforward from the last advances in classical planning.

>>>>

On the other hand, a striking figure of Table \ref{table:models_comparison2} that emphasizes a relevant feature of \FAMA is the small size of the training dataset it requires in comparison to other approaches. Unlike extensive-data ML approaches, our work explores an alternative research direction to learn sound models from small amounts of plan traces. This is an important advantage, particularly in domains in which it is costly or impossible to obtain a significant number of training samples. Unlike \CAMA, our approach does not require human intervention to label samples as it is able to learn from empty sequences of observed actions.

%very small datasets.

Finally, as it will be shown in section \ref{sec:experiments}, \FAMA is exhaustively evaluated, syntactically and semantically, over a wide range of domains (14 domains compared to the scarce number of tested domains of the rest of the approaches in Table \ref{table:models_comparison2}) and uses exclusively an \emph{off-the shelf} classical planner so it can benefit straightforward from the last advances in classical planning.
